---
title:  "Textual analysis of the book crime and punishment by Dostoevsky"
author: "Zarrin MINOOSEPEHR"
date:   " "
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Previously, when we wanted to choose a book to read, we used to read its summary first, then review a few random pages of the book to see if the content and feel of the book was what we were looking for or not. But now, as a student of computer science in the humanities, I realized that this can be done by science and even done much more accurately and completely, so I decided to do a textual analysis of Dostoevsky's book "Crime and Punishment" and compare the result with my own previous experience.

## Load the libraries we’ll be using
```{r load-libraries, warning=FALSE, message=FALSE}
library(gutenbergr) # For downloading books from Project Gutenberg
library(tidyverse) # For ggplot, dplyr, etc.
library(tidytext) # For generating insights from the literature, news and social media
library(cleanNLP) # For NLP analysis
```
## Get data 
By the means of **gutenbergr** package we can download the book. The book "crime and punishment" is in six parts, each part is divided to different chapters which in total we have 39 chapters. 
after downloading the book I have changed it to CSV file. Then I have cleaned the data and finally I have done some of the analysis chapter by chapter.
```{r get-books, echo=TRUE}
# 2554 crime_and_punishment
crime_and_punishment_original <- gutenberg_download(2554, meta_fields = "title")
write_csv(crime_and_punishment_original, "data/crime_and_punishment_original.csv")
```
```{r load-text, echo=TRUE}
read_csv("data/crime_and_punishment_original.csv")
```
## Clean up
```{r show-first-6-rows, echo=TRUE}
head(crime_and_punishment_original)
```

#using the cumsum() function to group by chapter for next analysis.
```{r clean-data}
crime_and_punishment <- crime_and_punishment_original %>% 
  # Get rid of rows where text is missing
  drop_na(text) %>% 
  # Automatically make chapter numbers
  mutate(chapter = str_detect(text, "^CHAPTER"),
         chapter_number = cumsum(chapter)) %>% 
  # Remove columns we don't need
  select(-gutenberg_id, -title, -chapter, )
```

## Tokens and counting words
```{r tidy-text-format}
word_frequencies <- crime_and_punishment %>%
  # The unnest_tokens() functions from tidytext counts words 
  # or bigram or paragraph to be in its own row
  unnest_tokens(word, text) %>% 
  # Remove stop words
  anti_join(stop_words) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  # Count all the words
  count(word, sort = TRUE)
```

```{r plot-top-15}
word_frequencies %>% 
  # Keep top 15
  top_n(15) %>%
  # Make the words an ordered factor so they plot in order
  mutate(word = fct_inorder(word)) %>% 
  ggplot(aes(x = n, y = word))+
  geom_col(fill="black")
```

## Bigrams

```{r tidy-bigrams}
crime_and_punishment_bigrams <- crime_and_punishment %>% 
  # n = 2 here means bigrams
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>% 
  # Split the bigrams into two words so we can remove stopwords
  separate(bigram, c("w1","w2"), sep = " ") %>% 
  filter(!w1 %in% stop_words$word,
         !w2 %in% stop_words$word) %>% 
  # Put the two word columns back together
  unite(bigram, w1, w2, sep = " ")
```

```{r counting-bigrams-plot-the-result}
bigram_frequencies <- crime_and_punishment_bigrams %>% 
  # Count all the bigrams
  count(bigram, sort = TRUE)
 
bigram_frequencies %>% 
  top_n(15) %>%
  mutate(bigram = fct_inorder(bigram)) %>% 
  ggplot(aes(x = n, y = bigram))+
  geom_col(fill="black") +
  labs(y = "Count", x = NULL, 
       title = "15 most frequent bigrams")
```


#Using cleanNLP package for this analysis.
In cleanNLP:
**cnlp_init_udpipe()**: Use an R-only tagger that should work without installing anything extra

```{r text-wrangling-with-dplyr}
# For the tagger to work, each row needs to be unique, which means we need to
# combine all the text into individual chapter-based rows. This takes a little
# bit of text-wrangling with dplyr:
crime_and_punishment_tag <- crime_and_punishment %>% 
  # Group by chapter number
  group_by(chapter_number) %>% 
  # Take all the rows in each chapter and collapse them into a single cell
  nest(data = c(text)) %>% 
  ungroup() %>% 
  # Look at each individual cell full of text lines and paste them together into
  # one really long string of text per chapter
  mutate(text = map_chr(data, ~paste(.$text, collapse = " "))) %>% 
  # Get rid of this column
  select(-data)
crime_and_punishment_tag
```

```{r nlp-tag, eval=FALSE}
# Use the built-in R-based tagger
cnlp_init_udpipe()
crime_and_punishment_tagged <- cnlp_annotate(crime_and_punishment_tag, 
                                     text_name = "text", 
                                     doc_name = "chapter_number")
write_csv(crime_and_punishment_tagged$token, "data/crime_and_punishment_tagged.csv")
```

```{r load-tagged-text, echo=TRUE}
crime_and_punishment_tagged <- read_csv("data/crime_and_punishment_tagged.csv")
```

```{r proper-nouns}
# Find all proper nouns
proper_nouns <- crime_and_punishment_tagged %>%
  filter(upos == "PROPN")

main_characters_by_chapter <- proper_nouns %>% 
  filter(lemma %in% c("Avdotya", "Sonia", "Katerina",
                      "Pyotr","Pulcheria", "Raskolnikov")) %>% 
  # Group by chapter and character name
  group_by(doc_id, lemma) %>% 
  # Get the count of mentions
  summarize(n = n()) %>% 
  # Make a new column named "name" that is an ordered factor of the names
  mutate(name = factor(lemma, levels = c("Avdotya", "Sonia", "Katerina",
                      "Pyotr","Pulcheria", "Raskolnikov"), ordered = TRUE)) %>% 
  # Rename this so it's called chapter
  rename(chapter = doc_id) %>% 
  # Group by chapter
  group_by(chapter) %>% 
  # Calculate the proportion of each name in each chapter
  mutate(prop = n / sum(n)) %>% 
  ungroup() %>% 
  # Make a cleaner chapter name column
  mutate(chapter_name = paste("Chapter", chapter)) %>% 
  mutate(chapter_name = fct_inorder(chapter_name))
main_characters_by_chapter
```

```{r props-plot, message = FALSE}
ggplot(main_characters_by_chapter, aes(x = prop, y = 1, fill = fct_rev(name))) + 
  geom_col(position = position_stack()) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_viridis_d(option = "plasma", end = 0.9, name = NULL) +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs(x = NULL, y = NULL,
       title = "Proportion of mentions of each character per chapter") +
  facet_wrap(vars(chapter_name), nrow = 5) +
  theme(legend.position = "top",
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill = "white"),
        legend.text = element_text(face = "bold", size = rel(1)),
        plot.title = element_text(face = "bold", hjust = 0.5, size = rel(1.7)),
        plot.subtitle = element_text(hjust = 0.5, size = rel(1.1)))
```

## Term frequency-inverse document frequency tf-idf

$$
\begin{aligned}
tf(\text{term}) &= \frac{n_{\text{term}}}{n_{\text{terms in document}}} \\
idf(\text{term}) &= \ln{\left(\frac{n_{\text{documents}}}{n_{\text{documents containing term}}}\right)} \\
tf\text{-}idf(\text{term}) &= tf(\text{term}) \times idf(\text{term})
\end{aligned}
$$

Here, to do this analysis, I add some other books of Dostoevsky

```{r Dostoevsky_selected_books}
Crime_and_punishment <- gutenberg_download(2554, meta_fields = "title")
Crime_and_punishment_clean <-Crime_and_punishment %>% 
      drop_na(text)

#The idiot
The_idiot <- gutenberg_download(2638	, meta_fields = "title")
The_idiot_clean <- The_idiot %>% 
    drop_na(text)
  # The Brothers Karamazov
The_Brothers_Karamazov <- gutenberg_download(28054, meta_fields = "title")
The_Brothers_Karamazov_clean <- The_Brothers_Karamazov %>% 
    drop_na(text)
# The Gambler	
The_Gambler <- gutenberg_download(2197, meta_fields = "title")
The_Gambler_clean <- The_Gambler %>% 
    drop_na(text)

```

```{r tidy-books}
# Use bind_rows() from dplyr to bind multiple data by row
Dostoevsky_selected_books <- bind_rows(The_idiot_clean, The_Brothers_Karamazov_clean, The_Gambler_clean, Crime_and_punishment_clean)
  
  book_words <- Dostoevsky_selected_books %>% 
    unnest_tokens(word, text) %>% 
    anti_join(stop_words) %>% 
    mutate(word = str_extract(word, "[a-z']+")) %>% 
    count(title, word, sort = TRUE)
```

```{r get-top-10-plot}
# find the words most distinctive to each document
book_words_tf_idf <-  book_words %>% 
  bind_tf_idf(word, title, n)
# Get the top 15 uniquest words
book_words_15 <- book_words_tf_idf %>% 
  arrange(desc(tf_idf)) %>% 
  group_by(title) %>% 
  top_n(15) %>% 
  ungroup() %>% 
  mutate(word = fct_inorder(word))
# Plot
ggplot(book_words_15, 
       aes(y = fct_rev(word), x = tf_idf, fill = title)) +
  geom_col() +
  guides(fill = FALSE) +
  labs(x = "tf-idf", y = NULL) +
  facet_wrap(~ title, scales = "free") +
  theme_bw()
```

## Sentiment analysis (sa)

To see what the different dictionaries look like using get_sentiments()
get_sentiments("afinn")  # Scoring system
get_sentiments("bing")  # Negative/positive
get_sentiments("nrc")  # Specific emotions
get_sentiments("loughran")  # Designed for financial statements; positive/negative

 
#Split into word tokens

```{r word-tokens}
crime_and_punishment_new <- crime_and_punishment %>%
  unnest_tokens(word, text)
```

#Join the sentiment dictionary

```{r sentiment-joining}
crime_and_punishment_sa <- crime_and_punishment_new %>%
  inner_join(get_sentiments("bing"))
```

Get a count of positive and negative words in each chapter. Convert the sentiment column into two columns named "positive" and "negative"

```{r plot-result}
sentiment_analysis_chapter <- crime_and_punishment_sa %>% 
  # Get a count of positive and negative words in each chapter 
  count(chapter_number, sentiment) %>% 
  # Convert the sentiment column into two columns named "positive" and "negative"
  pivot_wider(names_from = sentiment, values_from = n) %>% 
  # Calculate net sentiment
  mutate(net_sentiment = positive - negative)
  # Plot it
  sentiment_analysis_chapter %>% 
    ggplot(aes(x = chapter_number, y = net_sentiment)) +
    geom_line()
```

Another way, by splitting the data into groups of lines, to show a more granular view of the progression of the plot

```{r range-analysis}
sentiment_analysis_range <- crime_and_punishment_sa %>% 
  mutate(line_number = row_number()) %>% 
  # Divide lines into groups of 100
  mutate(index = line_number %/% 100) %>% 
  # Get a count of postiive and negative words in each 100-line chunk
  count(index, sentiment) %>% 
  # Convert the sentiment column into two columns named "positive" and "negative"
  pivot_wider(names_from = sentiment, values_from = n) %>% 
  # Calculate net sentiment
  mutate(net_sentiment = positive - negative)
  # Plot it
  sentiment_analysis_range %>% 
    ggplot(aes(x = index, y = net_sentiment)) +
    geom_col(aes(fill = net_sentiment > 0))
```

well, we see that the crime and punishment is a sad novel.

# Conclusion:
As a conclusion, I can say that the result is really close to my conclusion when I read it as a human being. A very sad story that deeply affected me. What I wish I could add to this analysis is the analysis of the books theme. I remember that in this book there were interesting questions and explanation about Justice, morality, love, rights, punishment, politics and poverty, etc. I wish I could find out which is bolder? Or in which category we can put this book? Is it just a literary novel? Or examining a moral and social theory? Or the psychological analysis of crime?
I hope in the future I can learn the way to do more precise text analysis.


### References

[Text Mining with R: Julia Silge and David Robinson](https://www.tidytextmining.com/)

[Dr. Andrew Heiss](https://datavizm20.classes.andrewheiss.com/example/13-example/)

[Project Gutenberg](https://www.gutenberg.org/ebooks/author/111)





